PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
changing ramp employment file name

## RAMP
### Read in data
```{r ramp employment cols}
if(RAMP == TRUE){
ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_coping_ramp.rds"))
dim(ramp.employment.raw)
colnames(ramp.employment.raw)
}
```

>>>>

## RAMP
### Read in data
```{r ramp employment cols}
if(RAMP == TRUE){
ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
dim(ramp.employment.raw)
colnames(ramp.employment.raw)
}
```
